Markov Chain Monte Carlo (MCMC)

### 2016-04-12 bayesian_statistics/MCMC/MCMC.Rmd
mcmc

---
title: "Markov Chain Monte Carlo"
date: "`r Sys.Date()`"
author: "Ming-Yu Liu"
output:
  rmdformats::readthedown:
    highlight: pygments
---

@@

		sample <- samples[ i - 1, ]

		for(j in 1:thin){

@@

			# flip a coin and accept the 
			# new proposal with probability min( ratio, 1 ),
			# if you don't accept the proposal,
			# then just keep what you had in the last step,
			# meaning nothing changed.
			# note that 1 is evaluated as TRUE
			if( rbinom( 1, size = 1, prob = min( ratios, 1 ) ) )
				sample <- proposal
		}
		samples[ i, ] <- sample
	}

	return( data.frame( samples[ (burnin + 1):iter, ] )	)
}

@@

>>>>

---
title: "Markov Chain Monte Carlo (MCMC)"
date: "`r Sys.Date()`"
author: "Ming-Yu Liu"
output:
  rmdformats::readthedown:
    highlight: pygments
---

@@

		sample <- samples[ i - 1, ]
		for(j in 1:thin){

@@

			# flip a coin and accept the 
			# new proposal with probability min( ratio, 1 ),
			# if you don't accept the proposal,
			# then just keep what you had in the last step,
			# meaning nothing changed.
			# note that 1 is evaluated as TRUE
			if( rbinom( 1, size = 1, prob = min( ratios, 1 ) ) )
				sample <- proposal
		}
		samples[ i, ] <- sample
	}
	return( data.frame( samples[ (burnin + 1):iter, ] )	)
}

@@

**Sources:**

Code to the documentation can be found [here](https://github.com/ethen8181/Business-Analytics/blob/master/bayesian_statistics/MCMC/MCMC.R).
